Towards open collaboration in biomedical and health research: A protocol for a scoping review of open collaboration

### 2025-01-08 doc/protocol.qmd
chore: :wrench: move authors back into their paper or protocol files

---
title: "Towards open collaboration in biomedical and health research: A protocol for a scoping review of open collaboration"
date: "2022-11-04"
doi: 10.17605/OSF.IO/K9DR5
execute:
  echo: false
---

>>>>

---
title: "Towards open collaboration in biomedical and health research: A protocol for a scoping review of open collaboration"
date: "2022-11-04"
author: 
  - name: Hannah Chatwin
    affiliations: 
      - ref: au
  - name: Mario Garcia
    affiliations: 
      - ref: ku
  - name: Daniel B. Ibsen
    affiliations: 
      - ref: sdca
      - ref: au
  - name: Luke W. Johnston
    affiliations: 
      - ref: sdca
      - ref: au
affiliations:
  - id: sdca
    name: Steno Diabetes Center Aarhus
    country: Denmark
  - id: au
    name: Aarhus University
    country: Denmark
  - id: ku
    name: Copenhagen University
    country: Denmark
doi: 10.17605/OSF.IO/K9DR5
execute:
  echo: false
---
